Draft Manuscript

### 2022-09-23 Prereg_and_manuscript/prereg.Rmd

**Study Information**
-

@@

**2.	Authors**
Emma Menchions – ORCid: https://orcid.org/0000-0003-2635-7043

@@

**Design Plan**
-

@@

**Sampling Plan**
-

@@

Data retrieved from (3): https://datadryad.org/stash/dataset/doi:10.5061%2Fdryad.4767v

- Abundance: According to Thiffault et al. (2016), the data on abundance of the 4 species were collected from 15,339 circular plots across central and northern Quebec along 1.5 – 2 km long transects of which supported 5-7 plots.

@@

**Variables**
-

@@

a.	Relative area of each forest type – (continuous)

b.	Useful precipitation (rain) (mm) (continuous) – I will consider this as annual rainfall

@@

1) Forest_Type 
    - I will categorize forest type based on the dominant two tree species in terms of relative area for each plot – to produce a variable with 3 possibilities (conifer, deciduous, mixed)

2) RainFall 
    - I will use the median annual rainfall for all plots as a cutoff value to define low and high precipitation

3) rf_index (rainfall-forest type index)
    - I will combine 1 and 2 into another categorical variable to assess the combined effects

**Analysis Plan**
-

@@

I will use the standard p-value criteria of p< 0.05 for determining significantly different means in the Kruskal-Wallis test (that the null hypothesis that all means are the same can be refuted)

@@

**References**
-

(1) Hornung, M. (1985). Acidification of soils by trees and forests. Soil Use and Management, 1(1), 24–27. https://doi.org/10.1111/j.1475-2743.1985.tb00648.x

(2) Soil Acidity—An overview | ScienceDirect Topics. (n.d.). Retrieved September 11, 2022, from https://www.sciencedirect.com/topics/earth-and-planetary-sciences/soil-acidity

(3) Thiffault, N., Grondin, P., Noël, J., & Poirier, V. (2015). Ecological gradients driving the distribution of four Ericaceae in boreal Quebec, Canada. Ecology and Evolution, 5(9), 1837–1853. https://doi.org/10.1002/ece3.1476

>>>>

## **Study Information**

@@

**2. Authors** Emma Menchions -- ORCid: <https://orcid.org/0000-0003-2635-7043>

@@

## **Design Plan**

@@

## **Sampling Plan**

@@

Data retrieved from (3): <https://datadryad.org/stash/dataset/doi:10.5061%2Fdryad.4767v>

-   Abundance: According to Thiffault et al. (2016), the data on abundance of the 4 species were collected from 15,339 circular plots across central and northern Quebec along 1.5 -- 2 km long transects of which supported 5-7 plots.

@@

## **Variables**

@@

a.  Relative area of each forest type -- (continuous)

b.  Useful precipitation (rain) (mm) (continuous) -- I will consider this as annual rainfall

@@

1)  Forest_Type
    -   I will categorize forest type based on the dominant two tree species in terms of relative area for each plot -- to produce a variable with 3 possibilities (conifer, deciduous, mixed)
2)  RainFall
    -   I will use the median annual rainfall for all plots as a cutoff value to define low and high precipitation
3)  rf_index (rainfall-forest type index)
    -   I will combine 1 and 2 into another categorical variable to assess the combined effects

## **Analysis Plan**

@@

I will use the standard p-value criteria of p\< 0.05 for determining significantly different means in the Kruskal-Wallis test (that the null hypothesis that all means are the same can be refuted)

@@

## **References**

(1) Hornung, M. (1985). Acidification of soils by trees and forests. Soil Use and Management, 1(1), 24--27. <https://doi.org/10.1111/j.1475-2743.1985.tb00648.x>

(2) Soil Acidity---An overview \| ScienceDirect Topics. (n.d.). Retrieved September 11, 2022, from <https://www.sciencedirect.com/topics/earth-and-planetary-sciences/soil-acidity>

(3) Thiffault, N., Grondin, P., Noël, J., & Poirier, V. (2015). Ecological gradients driving the distribution of four Ericaceae in boreal Quebec, Canada. Ecology and Evolution, 5(9), 1837--1853. <https://doi.org/10.1002/ece3.1476>
